Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-11-13 code/analysis.Rmd
messed with ANOVA but didn't end up using

@@

r2mod <- list()
r2val <- list()
ktval <- list()

@@

  r2mod[[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
  r2val[[k]] <- summary(r2mod[[k]])$r.squared
  ktval[[k]] <- -coef(r2mod[[k]])[2]

@@

@@

```{r message=FALSE, warning=FALSE}

@@

```{r warning=FALSE}

>>>>

###TEMP CODE!!!
#pumpfinal <- filter(pumpfinal, loc == "D")

@@

r2mod <- list()
r2val <- list()
ktval <- list()
resids <- list()

@@

  r2mod[[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
  r2val[[k]] <- summary(r2mod[[k]])$r.squared
  ktval[[k]] <- -coef(r2mod[[k]])[2]
  resids[[k]] <- cbind(tempdata,resid = resid(r2mod[[k]]))

@@

ANOVA:

resids <- tibble(bind_rows(resids))

residmod <- aov(data = resids, formula = resid ~ loc * ht)

resids %>%
  group_by(ht) %>%
  summarise(mean(resid), mean(abs(resid)), n(), sd(resid))

summary(residmod)

@@

```{r message=FALSE, warning=FALSE, eval=FALSE}

@@

```{r warning=FALSE, eval=FALSE}
